Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2023-08-18 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{multirow}
\usepackage{nicefrac}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage[inline]{enumitem}

@@

The most likely model parameters for the winning graph, corresponding to the mean of the marginals of the sampled posterior distributions, are tabulated in \cref{table:params}. We have fixed $p_\text{early}=0.3$ for early T-category tumors, and $t_\text{max}=10$ time steps). The result that $t_{23}$ and $t_{34}$ are relatively large compared to $b_3$ and $b_4$ reflects the observation that skip metastases in levels III and IV without involvement of the upstream level is rare. Since level II has no parent nodes except for the primary tumor, $b_2$ can be easily related to the prevalence of involvement in level II. The probability for no involvement of level II when the patient is diagnosed after $t$ time steps is $\left(1-b_2\right)^t$. The prevalence of level II involvement for late T-category patients is thus $1-\sum_{t=0}^{10} \left(1-0.37\right)^t 0.4^t \, (1-0.4)^{(10-t)}\binom{10}{t}\approx 0.8$, which agrees with \cref{fig:bg_prevalences}.

\begin{table}[]
    \centering
    % \variable{output/wg_means.tex}
    \caption{Mean of sampled parameters.}
    \label{tab:params}
\end{table}

@@

\ju{perhaps one could use the same color in each risk figure for a given clinical involvement, e.g. always green for N0}

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}
\usepackage{multirow}
\usepackage{nicefrac}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage[inline]{enumitem}
\usepackage{booktabs}

@@

The most likely model parameters for the winning graph, corresponding to the mean of the marginals of the sampled posterior distributions, are tabulated in \cref{table:params}. We have fixed $p_\text{early}=0.3$ for early T-category tumors, and $t_\text{max}=10$ time steps). The result that $t_{\text{II} \rightarrow \text{III}}$ and $t_{\text{III} \rightarrow \text{IV}}$ are relatively large compared to $b_\text{III}$ and $b_\text{IV}$ reflects the observation that skip metastases in levels III and IV without involvement of the upstream level is rare. Since level II has no parent nodes except for the primary tumor, $b_\text{II}$ can be easily related to the prevalence of involvement in level II. The probability for no involvement of level II when the patient is diagnosed after $t$ time steps is $\left(1-b_\text{II}\right)^t$. The prevalence of level II involvement for late T-category patients is thus
%
\begin{equation}
    \begin{aligned}
        \text{prev}_\text{late}^\text{II} &= 1-\sum_{t=0}^{10} \left(1-b_\text{II}\right)^t \cdot p_\text{late}^t \, (1-p_\text{late})^{(10-t)}\binom{10}{t} \\
        &\approx 0.8
    \end{aligned}
\end{equation}
%
which agrees with \cref{fig:bg_prevalences}.

\begin{table}[]
    \centering
    \variable{output/wg_means.tex}
    \caption{Mean of sampled parameters in percent.}
    \label{tab:params}
\end{table}

@@

\ju{perhaps one could use the same color in each risk figure for a given clinical involvement, e.g. always green for N0}
\rl{Done}
